---
title: "Profanity Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }
dbListTables(tm_db)
```

```{r querying}

dbGetQuery(tm_db, 'SELECT * FROM profanity LIMIT 5')
```

```{r}
teams_tbl <- dbGetQuery(tm_db, 'SELECT * FROM profanity')
teams_tbl

dim(teams_tbl)

summary(teams_tbl)

```

```{r}

library(tidyverse)

series_profanity <- teams_tbl %>% 
    group_by(series) %>%
    summarise(no_episodes = dplyr::n_distinct(episode),
    sum_profanity_series = dplyr::n()
                                   ) %>%
    mutate(profanity_per_episode = sum_profanity_series/no_episodes)


dbWriteTable(tm_db, "series_profanity", series_profanity)

#dbWriteTable(tm_db, "teams", teams)
#head(teams)
```


```{r}
dbListTables(tm_db)
```


```{r}


dbGetQuery(tm_db, "SELECT sp.*,
           ts.name, 
           ts.champion,
           tp.name as champion_name,
           ts.special,
           ts.episodes
           FROM series_profanity sp 
           LEFT JOIN series ts 
           ON sp.series = ts.id
           LEFT JOIN people tp
           ON sp.series = tp.series
           AND ts.champion = tp.id
          ")
```

```{r}
people_df <- dbGetQuery(tm_db, "SELECT * FROM people")
```
## Future Ideas
* Standard queries to join data into the most exhaustive/comprehensive dataset 
 ** Data at the (series, episode, task, contestant) level.
* Dashboard to provide insight as to when the database was last updated.
** What is the latest episode that we have data for?
** What is the latest ETL stamp.

You can also embed plots, for example:


```{r}
base_image_url <- "https://taskmaster.info/images/people/%s_%s.png"

#{tmi}_{name}.png

sprintf(base_image_url, 
sprintf("%04d", within_series_profanity$speaker_tmi),
gsub(" ", "_", tolower(within_series_profanity$speaker_name))
)


#0019_greg_davies_3.png"


```

```{r}
people_df
```

```{r}
base_image_url <- "https://taskmaster.info/images/people/%s_%s.png"

#{tmi}_{name}.png

contestant_base_url <- 
sprintf(base_image_url, 
sprintf("%04d", people_df$TMI),
gsub(" |-", "_", tolower(iconv(people_df$name, to = "ASCII//TRANSLIT")))
)


image_url_counter_gen <- function(x){
    gsub(".png", paste("_", x, ".png", sep =""), contestant_base_url)
}
    

image_url_counter_gen(5)


image_url_counter_matrix <- sapply(1:2, FUN = image_url_counter_gen)



#0019_greg_davies_3.png"


# https://taskmaster.info/images/people/0032_alex_horne_3.png

# https://taskmaster.info/images/people/0069_josh_widdicombe.png
# 
# 
# https://taskmaster.info/images/people/0049_jon_richardson.png
# 
# https://taskmaster.info/images/people/0052_katherine_ryan.png
# 
# https://taskmaster.info/images/people/0393_jenny_eclair_1.png
# 
# https://taskmaster.info/images/people/0394_kiell_smith_bynoe_1.png
# https://taskmaster.info/images/people/0378_dara_o_briain_1.png

```

```{r}
urls <-   c("http://www.amazon.com",
            "http://this.isafakelink.biz",
            "https://stackoverflow.com")

valid_url <- function(url_in,t=1){
  con <- url(url_in)
  check <- suppressWarnings(try(open.connection(con,open="rt",timeout=t),silent=T)[1])
  suppressWarnings(try(close.connection(con),silent=T))
  ifelse(is.null(check),TRUE,FALSE)
}

sapply(urls,valid_url)
```
```{r}
opts <- list(
     proxy         = "http://*******",
     proxyusername = "*****", 
     proxypassword = "*****", 
     proxyport     = 8080
)

```

```{r}
library(httr)

check_tm_url_png <- function(url_str, timeout_sec = 2)
{
    head_response <- httr::HEAD(url_str, httr::timeout(timeout_sec))
    head_status <- httr::http_status(head_response)
    
    url_exists <- head_status$message == httr::http_status(200)$message
    
    url_exists
}
```


```{r}
check_tm_url_png("https://taskmaster.info/images/people/0312_sophie_duker_1.png")
check_tm_url_png("https://taskmaster.info")
check_tm_url_png("https://www.google.com")
```


```{r}
temp <- sapply(image_url_counter_matrix, FUN = check_tm_url_png, USE.NAMES = FALSE)
```
#sapplyurl(image_url_counter_matrix[,1], valid_url)
```

```{r}
library(httr)
library(RCurl)
```

# Greg

```{r}
greg_profanity <- series_profanity %>% filter(series >= 1 &
                            speaker_id %in% c(2))
greg_profanity$image <- "https://taskmaster.info/images/people/0019_greg_davies_3.png"

ggplot(greg_profanity, aes(x=series, y = profanity_per_episode)) +     geom_line() +
geom_point() +
    geom_image(aes(image = image), size= 0.1) + 
    xlab("series") + ylab("Profanity Rate (Profanity per Episode)") +
    ggtitle("The Taskmaster's Potty Mouth")
```


```{r}

exp_overall_swear <- overall_swear_summary %>% mutate(
    prop_freq = freq/sum(freq),
    running_prop = cumsum(prop_freq)
    )



ggplot(
  exp_overall_swear,
  aes(
    label = word, size = prop_freq,
    colour = prop_freq <= 0.50
  )
) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 50) +
  theme_minimal()
```